HSC Synthetic Pipeline I: Basic Design and Characterization of the Photometric Performance of HSC

### 2017-04-10 draft/ms_v1.tex
Draft: PSF color

    As expected, we clearly see that the seeing condition impacts the \s2n{} of point
    sources at fixed input magnitude.
    In $i$-band, the \tract{} with slightly worse seeing (0.7\asec{}) shows systematically
    lower \s2n{} comparing to the one with better seeing (0.5\asec{}).
    As for the $g$-band, since the two \tracts{} share similar seeings now, they also
    follow similar relations.
    We also see that the blendedness can also affect accuracies of PSF photometry.
    In $i$-band, the highly blendend synthetic stars scatter toward lower \s2n{} at
    fixed magnitude.
    Interestingly, the effect is not obvious in $g$-band, suggeting the deblending
    process and photometric quality of blended objects also depend on seeing condition.

@@

    The overall performance of PSF photometry is excellent.
    In $i$-band, the median magnitude difference for \tract{} with 0.5\asec{} seeing is
    around ${\sim}0.015$ mag (${\sim}1.5$\% accuracy) at
    $i_{\mathrm{Input}}{\sim}19.0$ mag.
    At $i_{\mathrm{Input}}{\sim}24.0$ mag, the average accuracy of PSF
    magnitud keeps at ${\sim}3$\% level (${\sim}0.036$ mag average difference).
    Down to $i_{\mathrm{Input}}{\sim}25.2$ mag, the average accuracy descreases to
    ${\sim}7$\% level with an average ${\sim}0.072$ mag difference.
    The \tract{} with worse seeing shows similar accuracy of PSF photometry at
    $i_{\mathrm{Input}}<23.5$ mag.
    At faint end, the accuracy becomes slightly worse: ${\sim}5$\% accuracy around
    $i_{\mathrm{Input}}{\sim}24.0$ mag; and ${\sim}11$\% accuracy around
    $i_{\mathrm{Input}}{\sim}25.2$ mag.
    \citet{HSCDR1} evaluates the accuracy of PSF photometry via external comparisons
    with the PS1 PV2 and SDSS data at $i<21$ mag, and finds a 1-2\% level accuracy,
    which is consistent with our results.
    At fainter magnitude, external comparisons become difficult due to the lack of deep
    imaging data at HSC level and the impact of the color-term when comparing photometry
    using different filters.
    The results from \synpipe{} hence provide more useful evaluations down to the
    detection limit\footnote{Strictly speaking, the uncertainties here should be
    considered as lower limit as the \synpipe{} now does not consider the uncertainties
    in PSF modeling.}.

@@

    For relative isolated stars, \hscpipe{} provides unbiased PSF photometry down to
    very faint magnitude in $i$- and $z$-band.
    For $g$-, $r$-, and $y$-band, we find small offsets in the distributions of magnitude
    differences, which indicates \hscpipe{} tends to underestimate the fluxes of stars
    in these bands by ${\sim}0.01-0.02$ mag.
    Although the exact cause of this offset is unclear (could still be related to
    differenecs in seeing), it will not affect the accuracies of magnitudes of colors.

    At the same time, the story for highly blended stars is very different.
    \hscpipe{} on average systematically underestimates the total fluxes of them by
    $0.05$--$0.10$ mag at fixed input magnitude.
    We see the same effect in all bands, and the impact of blendedness becomes
    increasingly significant at fainter magnitde.
    It is therefore important to keep this in mind when using PSF photometry for point
    sources in HSC data.

@@

        \item \plan{Briefly explain why PSF colors are important; we focus on the
            \forced{} PSF colors here}

        \item The results for accuracy of \forced{} PSF colors are shown in
            Fig \ref{fig:psf_color} and Fig \ref{fig:psf_cdist}.

        \item \plan{In Fig \ref{fig:psf_color}, we investiage how \forced{}
            PSF colors depend on input magnitude and colors using both $(g-i)$ and
            $(i-y)$ colors.
            Results suggest \hscpipe{} \forced{} PSF photometry can provide
            accurate and unbiased colors for stars in our tests.
            The uncertainties do not show any significant dependence on neither input
            magnitude nor color.}

        \item \plan{For $(g-i)$ color, average uncertainty around
            $i_{\mathrm{Input}}{\sim}19.0$ mag is ${\sim}0.025$ mag.
            The uncertainty increases to ${\sim}0.11$ mag at
            $i_{\mathrm{Input}}{\sim}25.0$ mag.
            Results for $(i-y)$ color is similar.}

        \item \plan{In Fig \ref{fig:psf_cdist}, we use the results from the bad
            seeing \tract{} to show that the \forced{} PSF photometry
            can accurately recover the color-color sequences of stars down to
            $i{\sim}25$ mag.}

        \item \plan{Accuracy of \forced{} PSF photometry apparently does not
            strongly depend on seeing condition.
            Impact from blendedness on PSF color is less serious than the magnitude,
            although highly blended stars still show worse color accuracy and
            systematically bluer (redder) $(g-i)$ ($i-y$) colors.
            \unforced{} PSF photometry show similar but slightly worse
            accuracy than the \forced{} ones. }

@@

    \plan{Briefly explain the definition of blendedness}

    \plan{Relationship between magnitude and blendedness}

>>>>

    As expected, we clearly see that the seeing condition impacts the \s2n{} of point
    sources at fixed input magnitude.
    In $i$-band, the \tract{} with slightly worse seeing (0.7\asec{}) shows systematically
    lower \s2n{} comparing to the one with better seeing (0.5\asec{}).
    As for the $g$-band, since the two \tracts{} share similar seeings now, they also
    follow similar relations.
    We also see that the blendedness can also affect accuracies of PSF photometry.
    In $i$-band, the highly blended synthetic stars scatter toward lower \s2n{} at
    fixed magnitude.
    Interestingly, the effect is not obvious in $g$-band, suggesting the deblending
    process and photometric quality of blended objects also depend on seeing condition.

@@

    The overall performance of PSF photometry is excellent.
    In $i$-band, the median magnitude difference for \tract{} with 0.5\asec{} seeing is
    around ${\sim}0.015$ mag (${\sim}1.5$\% accuracy) at
    $i_{\mathrm{Input}}{\sim}19.0$ mag.
    At $i_{\mathrm{Input}}{\sim}24.0$ mag, the average accuracy of PSF
    magnitude keeps at ${\sim}3$\% level (${\sim}0.036$ mag average difference).
    Down to $i_{\mathrm{Input}}{\sim}25.2$ mag, the average accuracy decreases to
    ${\sim}7$\% level with an average ${\sim}0.072$ mag difference.
    The \tract{} with worse seeing shows similar accuracy of PSF photometry at
    $i_{\mathrm{Input}}<23.5$ mag.
    At faint end, the accuracy becomes slightly worse: ${\sim}5$\% accuracy around
    $i_{\mathrm{Input}}{\sim}24.0$ mag; and ${\sim}11$\% accuracy around
    $i_{\mathrm{Input}}{\sim}25.2$ mag.
    \citet{HSCDR1} evaluates the accuracy of PSF photometry via external comparisons
    with the PS1 PV2 and SDSS data at $i<21$ mag, and finds a 1-2\% level accuracy,
    which is consistent with our results.
    At fainter magnitude, external comparisons become difficult due to the lack of deep
    imaging data at HSC level and the impact of the color-term when comparing photometry
    using different filters.
    The results from \synpipe{} hence provide more useful evaluations down to the
    detection limit\footnote{Strictly speaking, the uncertainties here should be
    considered as lower limit as the \synpipe{} now does not consider the uncertainties
    in PSF modeling.}.

@@

    For relative isolated stars, \hscpipe{} provides unbiased PSF photometry down to
    very faint magnitude in $i$- and $z$-band.
    For $g$-, $r$-, and $y$-band, we find small offsets in the distributions of magnitude
    differences, which indicates \hscpipe{} tends to underestimate the fluxes of stars
    in these bands by ${\sim}0.01-0.02$ mag.
    Although the exact cause of this offset is unclear (could still be related to
    differences in seeing), it will not affect the accuracies of magnitudes of colors.

    At the same time, the story for highly blended stars is very different.
    \hscpipe{} on average systematically underestimates the total fluxes of them by
    $0.05$--$0.10$ mag at fixed input magnitude.
    We see the same effect in all bands, and the impact of blendedness becomes
    increasingly significant at fainter magnitude.
    It is therefore important to keep this in mind when using PSF photometry for point
    sources in HSC data.

@@

    Color measurement based on PSF photometry is the most appropriate one for point
    sources, and is therefore important to many scientific goals of the HSC survey
    (e.g. study of the Milky Way structure, selection of unique stellar objects or
    high-redshift quasars, and the accurate star--galaxy separation).

    In Fig \ref{fig:psf_color}, we evaluate the accuracies of the \forced{} $(g-i)$
    and $(i-y)$ PSF colors via comparing the error in color measurements with both
    input magnitudes and input colors.
    These results suggest that \hscpipe{} provides accurate and unbiased PSF color
    estimates for synthetic stars with realistic color distributions down to very faint
    magnitude.
    For $(g-i)$ color, the average uncertainty around $i_{\mathrm{Input}}{\sim}19.0$ mag
    is ${\sim}0.025$ mag, and increases to ${\sim}0.11$ mag at
    $i_{\mathrm{Input}}{\sim}24.0$ mag.
    The results are very similar for the $(i-y)$ color.
    We also find that the accuracies of PSF colors do not depend on the input colors of
    the synthetic stars or the seeing conditions.
    For instance, the accuracy of $(g-i)$ color for \tract{} with bad seeing only becomes
    slightly worse in the very faint end (${\sim}0.14$ mag at
    $i_{\mathrm{Input}}{\sim}24.0$ mag) comparing to the results for good seeing \tract{}.

    We further illustrate the accuracies of PSF colors via comparing the distributions
    of colors for the input synthetic stars and the ones recovered by \hscpipe{}
    (see Fig \ref{fig:psf_cdist}).
    Using four different colors and two color--color planes, we show that the \forced{}
    PSF colors can accurately reproduce the distributions of all four colors and the
    2-D color-color distributions.

    As for the highly blended stars, on Fig \ref{fig:psf_color}, we see that on average
    they still have larger uncertainties in colors comparing to the relative isolated
    ones.
    For $(g-i)$ color, the average color uncertainty is ${\sim}0.1$ mag larger for the
    highly blended stars at fixed input magnitude.
    However, the biases in color measurements for these stars are less severe than
    the magnitude measurements.
    Although the blended stars still show slightly bluer (redder) $(g-i)$ ($(i-y)$)
    colors comparing to the isolated ones and the input values, the differences in the
    distributions of color uncertainties of blended and isolated stars are less striking
    than the ones for magnitude differences.

@@

    \plan{Review the definition of blendedness and explain why it is important.}
    \plan{Relationship between magnitude and blendedness}
